Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-21 report/report.tex
Cite Todor
Summary of Todor's viewpoint in Background

Procedural modeling of road networks is of interest to the fields of urban planning and urban architecture. In recent years there has been an advent of interactive tools that aid urban planners in placing or generating features of an urban plan, particularly roads and road networks.
Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling.

Motivation

Navigation agents, they might fail navigating when faced with a too narrow path or intersecting obstacles
Using a road network to creates an underlying navmesh

@@

\section{Related work}
Fan et al, 2015
Kunze, 2012 (reference in Fan et al)

@@

>>>>

Procedural modeling of road networks is of interest to the fields of urban planning and urban architecture. In recent years there has been an advent of interactive tools that aid urban planners in placing or generating features of an urban plan, particularly roads and road networks. Procedural and AI solutions that aid the arcitect in a form of human-machine symbiosis.

The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are CityEngine (made by the startup Procedural, bought by ESRI), Urban Canvas (made by the startup Synthicity, bought by Autodesk) and ArcGIS (***).

But such tools are as of today not commonly applied in urbanist practises, due to failures in reflecting the unique workspace of arcitects and their design needs. Urban arcitecture is a social factors, stakeholders. Each arcitect is an actor in a continously developing environment, and affecting that environment in a complex manner through their action.

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.

Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.

(Stojanivski, 2020)

Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling.
Navigation agents, they might fail navigating when faced with a too narrow path or intersecting obstacles
Using a road network to creates an underlying navmesh

@@

\section{Related work}
Fan et al, 2015
Kunze, 2012 (reference in Fan et al)
Haklay

@@

\bibitem{stojanovski-20}
Stojanivski T. 2020. Viewpoint: City Information Modeling (CIM) And Digitizing Urban Design Practises.
Under review
